---
title: "Financial Data Analysis"
author: "Lounès AÏT KARROU"
format: html
editor: visual
---
```{r}
#| message: false
here::i_am("dplyr-102.Rproj")
library(here)
library(vroom)
library(dplyr)
library(tidyr)
library(ggplot2)
```

## Data loading

```{r}
#| message: false
client <- vroom("data/client.csv")
accounts <- vroom("data/account.csv")
disp <- vroom("data/disp.csv")
```

## Joining data tables
A cllection of joining functions of the form `*_join`.   
   
### Inner join
```{r}
da <- inner_join(accounts,disp)
```
We observe that there is some kind of repitition, more redondant than the original data (e.g: line 2 and 3 are quite similar)

```{r}
cda <- inner_join(client, da) #We can't join multiple table, we have to do it progressivly
```
The problem here is that `district_id` is part of both DB but are not representing the same thing. Hence we have to differenciate them :

```{r}
cda <- inner_join(client, da, by=join_by(client_id), suffix=c("_home", "_bank"))
```

Here we have 2 `disctrict_id`, one for the client and the other for the bank.   
   
### Home disttric versus bank disctrict

```{r}
home_diff_bank <- cda |> filter(district_id_home != district_id_bank) |> nrow()
```

We observe that `r home_diff_bank` clients have a bank in another district as the one they live in. 

```{r}
cda |> 
  group_by(account_id) |>
  distinct(district_id_home) |>
  summarise(N=n()) |>
  filter(N>1)
```

### Gender gap ?
```{r}
client |> count(gender)
```
We see an almost perfect balance between Male and Female. 

```{r}
client |> 
  ggplot(aes(y=gender)) + geom_bar()
```
```{r}
# Other way to have the same graph : 
client |> 
  ggplot(aes(x=gender)) + geom_bar() + coord_flip()
```

```{r}
cda |>
  count(gender, type)
```
 
It seems that there is no gender gap at first.    
   
```{r}
cda |>
  count(gender, type) |>
  group_by(gender) |>
  mutate(freq=n/sum(n)) |>
  select(-n) |>
  ungroup() |>
  pivot_wider(values_from=freq, names_from=type)
```
```{r}
cda |>
  ggplot(aes(y=gender, fill=type)) + geom_bar(position="fill")
```


```{r}
chisq.test(cda |> pull(gender),
           cda |> pull(type))
```





