---
title: "Financial Data Analysis"
author: "Lounès AÏT KARROU"
format: html
editor: visual
---
```{r}
#| message: false
here::i_am("dplyr-102.Rproj")
library(here)
library(vroom)
library(dplyr)
library(tidyr)
library(ggplot2)
```

## Data loading

```{r}
#| message: false
client <- vroom("data/client.csv")
accounts <- vroom("data/account.csv")
disp <- vroom("data/disp.csv")
```

## Joining data tables
A cllection of joining functions of the form `*_join`.   
   
### Inner join
```{r}
da <- inner_join(accounts,disp)
```
We observe that there is some kind of repitition, more redondant than the original data (e.g: line 2 and 3 are quite similar)

```{r}
cda <- inner_join(client, da) #We can't join multiple table, we have to do it progressivly
```
The problem here is that `district_id` is part of both DB but are not representing the same thing. Hence we have to differenciate them :

```{r}
cda <- inner_join(client, da, by=join_by(client_id), suffix=c("_home", "_bank"))
```

Here we have 2 `disctrict_id`, one for the client and the other for the bank. 





